Quantile Regressions via Method of Moments with multiple fixed effects

### 2023-10-27 article/article.qmd
update
article

@@

In this framework, our paper expands on @mss2019, following some of the suggestions by the authors regarding further research. First, making use of the properties of GMM estimators, we derive various alternatives for the estimation of standard errors based on the empirical Influence functions of the estimators. Second, we reconsider the application of Frisch–Waugh–Lovell (FWL) theorem (@frishwaugh1933 and @lovell1963) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.

@@

$$Q(Y|X,\tau) =X\beta(\tau)
$${#eq-eq1}

@@

$$Q(Y|X,\tau) =X\beta+X\gamma(\tau)
$${#eq-eq2}

@@

$$\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
$${#eq-eq3}

@@

$$y_i=x_i'\beta+\varepsilon_i \times x_i'\gamma(\tau)
$${#eq-eq4}

@@

@@

$$Q(Y|X,\tau) =X\beta+X\gamma \times Q(\varepsilon|\tau)
$${#eq-eq5}

@@

$$\beta(\tau) = \beta + \gamma \times Q(\varepsilon|\tau)
$${#eq-eq6}

While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model. First, because the location and scale model can be identified globally, with only a single parmater ($Q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000). Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.

Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a method of moments approach. And while its possible to identify all coefficients ($\beta,\gamma, Q(\varepsilon|\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.

1. The location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic. In this case, the location model coefficients are identified under the following condition:
$$\begin{aligned}
  y_i &=x_i'\beta+u_i \\
  E[u 'X ] &=0
  \end{aligned}
$${#eq-eq7}

@@

$$\begin{aligned}
  |u_i| &=x_i'\gamma+v_i \\
  E[ (|u|-X \gamma) X ] &=0
  \end{aligned}
$${#eq-eq8}

@@

$$\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma Q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
$${#eq-eq9}

Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma Q(\varepsilon|\tau)$. Afterwords, the conditional quantile coefficients is simply defined as the combination of the location and scale coefficients.

@@

$$\begin{aligned}
  E[u_i x_i ] &= E[h_{1,i}]=0 \\
  E[ (|u_i|-x_i \gamma) x_i ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
$${#eq-eq10}

@@

Call $\theta=[ \beta' \ \ \gamma'  \ \ Q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified in @eq-eq10, a just identified model.  And the function $h_i$ is a vector function that stacks all the moments at the individual level described in @eq-eq10. Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as:
$$
\hat{V}(\hat\theta)=\frac{1}{N} 
\bar G(\hat\theta)^{-1} 
\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
\bar G(\hat\theta)^{-1} 
$$

where the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.

@@

This is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.

In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+Q(\varepsilon,\tau)\gamma$ and variance-covariance matrix equal to:

@@

$$\Xi = [ I(k), \hat Q(\varepsilon|\tau) \cdot I(k), \hat \gamma ]
$$

@@

@@

@@

@@

$$q(y|\tau,X) = x(\beta + q(e|\tau) \times \gamma)$$

@@

In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q(\varepsilon|\tau)']$, we need to obtain the influence functions of all coefficients, which are defined as:

@@

$$h_{3,i} = \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau$$

@@

$$h_{3,i} \approx I\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$

@@

$$\begin{aligned}
\bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
\end{aligned}
$$

@@

$$\begin{aligned}
E(K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) \\
&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\varepsilon|\tau)) \\
\end{aligned}
$$

@@

$$\bar G_{3,1} &= -N^{-1} f_{\varepsilon}\big(q(\varepsilon|\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
$$

Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$.[^6] Thus, we can rewrite the last term as:

[^6:] This approximation will be useful when we consider the estimation of the influence functions.
$$\bar G_{3,1} = - f_{\varepsilon}\big(q(\varepsilon|\tau)\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
$$

@@

$$\begin{aligned}
\bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) q(\varepsilon,\tau) x_i' \\
             &=-N^{-1} \sum f_{y|x}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta ) q(\varepsilon,\tau) x_i' \\
             &=-N^{-1} f_{\varepsilon}(q(\varepsilon|\tau)) q(\varepsilon,\tau) \sum \frac{x_i'}{x_i'\gamma} \\
             &=- f_{\varepsilon}(q(\varepsilon|\tau)) q(\varepsilon,\tau) \frac{\bar x_i'}{\bar x_i'\gamma}
\end{aligned}
$$

@@

$$\begin{aligned}
\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\varepsilon|\tau)} \\
 &= -\frac{1}{N} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
 &= -\frac{1}{N} \sum f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
 &= -\frac{1}{N} \sum f_{\varepsilon}(q(\varepsilon|\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
 &= - f_{\varepsilon}(q(\varepsilon|\tau)) 
\end{aligned}
$$

### Influence functions

**Location coefficients**:

@@

**Scale Coefficients coefficients**:

$$\begin{aligned}
\lambda_i(\gamma)&=\bar G_{22}^{-1}\Big(h_{2i}-\bar G_{21} \lambda_i(\beta)\big) \\
&=N (X'X)^{-1}(x_i(|\nu_i|-x_i' \gamma))
-  N E(sign(\nu_i))  (X'X)^{-1} x_i R_i \\
&= N(X'X)^{-1} x_i \Big(2 R_i \big[1(R_i \geq 0) - E(1(R_i \geq 0)) \big]  -x_i'\gamma \Big) \\
&= N(X'X)^{-1} x_i (\tilde R_i  -x_i'\gamma )
\end{aligned}
$$

# References {-}

>>>>

<!--
How to Render this?
Lik this:
quarto render article.qmd --to elsevier-pdf

-->

@@

In this framework, our paper expands on @mss2019, following some of the suggestions by the authors regarding further research. First, making use of the properties of GMM estimators, we derive various alternatives for the estimation of standard errors based on the empirical Influence functions of the estimators. Second, we reconsider the application of Frisch--Waugh--Lovell (FWL) theorem (@frishwaugh1933 and @lovell1963) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.

@@

$$q(Y|X,\tau) =X\beta(\tau)
$$ {#eq-eq1}

@@

$$q(Y|X,\tau) =X\beta+X\gamma(\tau)
$${#eq-eq2}

@@

$$\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
$$ {#eq-eq3}

@@

@@

$$\begin{aligned}
y_i &=x_i'\beta+\nu_i \\
\nu_i &=\varepsilon_i \times x_i'\gamma 
\end{aligned}
$$ {#eq-eq4}

@@

$$q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
$$ {#eq-eq5}

@@

$$\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
$$ {#eq-eq6}

While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model. First, because the location and scale model can be identified globally, with only a single parmater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000). Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.

Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a method of moments approach. And while its possible to identify all coefficients ($\beta,\gamma, q(\varepsilon|\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.

1.  The location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic. In this case, the location model coefficients are identified under the following condition:

$$\begin{aligned}
      y_i &=x_i'\beta+\nu_i \\
      E\big[ x_i \nu_i\big] &=0
      \end{aligned}
$$ {#eq-eq7}

@@

$$\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
  E\big[ x_i \omega_i \big] &=0 \\
  E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
$$ {#eq-eq8}

@@

$$\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
$$ {#eq-eq9}

Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)$. Afterwords, the conditional quantile coefficients is simply defined as the combination of the location and scale coefficients.

@@

$$\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
$$ {#eq-eq10}

@@

Call $\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified by the modement conditions in @eq-eq10, a just identified model. And the function $h_i$ is a vector function that stacks all the moments at the individual level described in @eq-eq10. Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as:

$$
\hat{V}(\hat\theta)=\frac{1}{N} 
\bar G(\hat\theta)^{-1} 
\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
\bar G(\hat\theta)^{-1} 
$$

Which is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.

Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.

@@

In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma$ and variance-covariance matrix equal to:

@@

$$\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
$$

@@

While it is possible to estimate the variance-covariance matrix using simultaneous model estimation, for a just identified model, it is more efficient to estimate each set of coefficients separately. The variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).

1. Need to add the general condition Var=(inf (theta) * inf(theta))

Thatn inf(theta) = inf beta gamma and q)tay

and finally define what the IFs are (see appendix)

@@

### Robust Standard Errors

Cross product of IFs

### Clustered Standard Errors

Sun then cross product

### GLS Standard Errors

Original paper;

@@

## Model Identification

@@

$$q(y|\tau,X) = x(\beta + q(\varepsilon |\tau) \times \gamma)$$

@@

For simplicity, for the rest of the appendix, I will use $q^\varepsilon_\tau$ to represent $q(\varepsilon |\tau)$.

## Estimation of the variance-covariance matrix

In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as:

@@

$$\begin{aligned}
h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) - \tau \\
\end{aligned}
$$

@@

$$h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$

@@

$$\begin{aligned}
\bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'
\end{aligned}
$$

@@

$$\begin{aligned}
E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
\end{aligned}
$$

@@

$$\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
$$

Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$. [^6] Thus, we can rewrite the last term as:

$$\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
$$

[^6]: This approximation will be useful when we consider the estimation of the influence functions.

@@

$$\begin{aligned}
\bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) q^\varepsilon_\tau x_i' \\
             &=-N^{-1} \sum f_{y|x}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta ) q^\varepsilon_\tau x_i' \\
             &=-N^{-1} f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \sum \frac{x_i'}{x_i'\gamma} \\
             &=- f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma}
\end{aligned}
$$

@@

$$\begin{aligned}
\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q^\varepsilon_\tau} \\
 &= -\frac{1}{N} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
 &= -\frac{1}{N} \sum f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) x_i'\gamma \\
 &= -\frac{1}{N} \sum f_{\varepsilon}(q^\varepsilon_\tau) \frac{x_i'\gamma}{ x_i'\gamma} \\
 &= - f_{\varepsilon}(q^\varepsilon_\tau) 
\end{aligned}
$$

## Influence functions

### Location coefficients

@@

Which can also be written as a function of the standardized residuals:

$$\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i ( x_i'\gamma \times \varepsilon))
$$

### Scale Coefficients coefficients**

$$\begin{aligned}
\lambda_i(\gamma)&=\bar G_{2,2}^{-1}\Big(h_{2,i}-\bar G_{2,1} \lambda_i(\beta)\Big) \\
&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) 
- N^{-1} E[sign(\nu_i)] X'X \big[ N (X'X)^{-1}(x_i \nu_i) \big] \Big) \\
&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) - E[sign(\nu_i)] (x_i \nu_i)  \Big) \\
&=N (X'X)^{-1} x_i \Big( |\nu_i| - E[sign(\nu_i)] \nu_i -x_i' \gamma \Big) 
\end{aligned}
$$

However,

$$\begin{aligned}
|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times \mathbb{1}(\nu_i < 0) \\
|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times [1-\mathbb{1}(\nu_i \geq 0)] \\
|\nu_i| &= 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  
\end{aligned}
$$

And
$$\begin{aligned}
E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[(1-\mathbb{1}(\nu_i \geq 0))] \\
E[sign(\nu_i)] &= 2 E[\mathbb{1}(\nu_i \geq 0)] - 1
\end{aligned}
$$

Thus,

$$\begin{aligned}
\lambda_i(\gamma) &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  - ( 2 E[\mathbb{1}(\nu_i \geq 0)] - 1) \nu_i -x_i' \gamma \Big) \\
  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) -  2 E[\mathbb{1}(\nu_i \geq 0)] \nu_i -x_i' \gamma \Big) \\
  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \big[ \mathbb{1}(\nu_i \geq 0) -  E[\mathbb{1}(\nu_i \geq 0)] \big] -x_i'\gamma \Big) \\
  &= N(X'X)^{-1} x_i   \Big( \tilde \nu_i -x_i' 
  \gamma \Big)
\end{aligned}
$$

This last expression is the equivalent simplification used in @mss2019 and @im2000. If the scale function is strictly possitive, it also follows that $\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)$. Thus, it can be simplified as:

$$\begin{aligned}
\lambda_i(\gamma) &= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)
\end{aligned}
$$

### Quantile of standardized residual

$$\begin{aligned}
\lambda_i(q^\varepsilon_\tau)&=\bar G_{3,3}^{-1}
\Big(
 h_{3,i}-\bar G_{3,1} \lambda_i(\beta)-\bar G_{3,2} \lambda_i(\gamma)
\Big) \\
&=-\frac{1}{f_{\varepsilon}(q^\varepsilon_\tau)} \times \Bigg( \Big(\mathbb{1} ( q^\varepsilon_\tau  \geq \varepsilon  ) - \tau \Big)  \\
&+ f_{\varepsilon} (q^\varepsilon_\tau) \frac{\bar x_i'}{\bar x_i'\gamma} 
N (X'X)^{-1} x_i  ( x_i'\gamma \times \varepsilon) \\
&+ f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
  \gamma \big) 
\Bigg) \\
&=\frac{\tau-\mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) }{f_{\varepsilon}(q^\varepsilon_\tau)}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q^\varepsilon_\tau \frac{ \tilde \nu_i -x_i' 
  \gamma }{\bar x_i'\gamma} 
\end{aligned}
$$

# References {.unnumbered}
